---
title: "ReBird"
date: "September 19, 2019"
author: "Lauren Chan"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Tests with ReBird

Testing some of the functionality of ReBird to download appropriate records.

Using `rebird v1.0.3`

Load libraries
```{r}
library(rebird)
```
Store keys and loc in variables to make it a little easier to call them.


```{r}
mykey <- "96h4mi8jusor"
fernhill <- "L163529"
```

The following code will get data for a particular date from Fernhill. The `fieldSet="full"` is necessary to get all 27 columns of data. Otherwise, only get 12. Binding of tables is clunky.
```{r eval=FALSE}
oct1 <- ebirdhistorical(loc=fernhill, date="2016-10-01", key=mykey, fieldSet = "full")
oct2 <- ebirdhistorical(loc=fernhill, date="2016-10-02", key=mykey, fieldSet = "full")

twodays <- rbind(oct1, oct2)
```

## Date formats are strings as YYYY-MM-DD that need to be converted to date format using `as.Date()`
```{r}
a.date <- as.Date("2018-10-01")  
```

## We can create a function to get the records

This function takes start date and end date as strings. 


For i in the range of dates, proceeding one day at a time we grab records. They are stored in `daydat` and we bind this to the everygrowing `dat` variable that is holding all the records gathered so far. 
```{r}
myrecords <- function(start, end){     # start and end dates as YYYY-MM-DD strings
  startdate <- as.Date(start)          # convert to date format
  enddate <- as.Date(end)
  dat<-NULL                            # make sure storage table is empty
  
  # for loop sequences through the dates. When date is stored in `i` it is in funny format
  # need to convert first setting origin (1970-01-01" is what R uses as default)
  for (i in seq.Date(startdate, enddate, 1)){
    thedate <- as.Date(i, origin="1970-01-01")
    daydat <- ebirdhistorical(loc=fernhill, date=thedate, key=mykey, fieldSet = "full")
    dat<- rbind(dat,daydat)
  }
  dat
}
```

```{r}
myrecords("2018-10-01", "2018-10-05")
```


